Regional and Urban Economics

### 2023-02-19 Retail Agglomeration_Theory.qmd
Ferdig med abstract håper at resultatet stemmer lol

`The topic of research (What was studied)`

`The purpose (What was done)`

`The methodology (how the research was done)`

`Main findings (what was found)`

`Policy and implications (significance of findings)`

@@

`A brief description of the problem and its importance`

>>>>

There are several factors to take in to consideration when deciding where a dental practice should be located.
Spatial competition is a critical consideration in regional economics.
Some of the factors influencing the decision making is retail agglomeration attributes, spatial monopoly and the attractiveness of a particular place of interest.
This study aims to examine the dental industry and find the strategy most profitable for the dental industry.

The study utilize a quantitative research approach, employing spacial explanatory data analysis techniques to determine the location decisions of firms.
Geographical data was collected from locations in Norway showing all dentists, central places, retail agglomeration and other points of interest such as the government regulated wine monopoly.
Spatial regression analyses was used to identify the factors influencing the location decisions of firms.

Furthermore, the result indicates the distance to retail agglomeration areas and central places playes a significant role in the location decisions for firms.
Firms are more likely to locate closer to these areas, which offer access to a larger customer base and lower cost of transportation.
However, the results also suggest other factors, such as market size and completion also influence the location decisions for firms.

The studies findings have particular implications for policy-makers, developer, and dental practises seeking to maximize profits through strategic decisions.
By understanding the importance of proximity to retail agglomeration areas and central places, these stakeholders can make informed decisions that benefit the local economy and improve competitiveness of the region.
Perhaps more importantly prevent agrassive retail agglomeration areas from "killing down town".

@@

`A brief description of the problem and its importance CHECK`
